Artificial ecosystem selection reveals relationships between microbiome composition and ecosystem function

### 2022-12-06 analysis/analysis.Rmd
reorganize working directory and add new analysis and text

---
title: "Community Analysis"
author: "Andrew Morris"
date: "6/28/2022"
output: 
  html_document:
    toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = TRUE)
knitr::opts_knit$set(root.dir=normalizePath('../'))
set.seed(1337)

@@

```{r initialize_packages}

library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(broom)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)

source('R/functions.R')

@@

```{r import-data}

aes_data <- read_tsv('Output/community_data.tsv')

@@

@@

```{r remove_chloroplasts}

@@

@@

# Exploratory

@@

a_analysis %>%
  select(sample, n_seqs, sobs, rare) %>%
  pivot_longer(-c(sample, n_seqs)) %>%
  ggplot(aes(x=n_seqs, y=value, color=name)) +
  geom_point() +
  geom_smooth(se=FALSE) +
  coord_cartesian(ylim=c(0, 6000)) +
  theme_classic() +
  labs(x = "Sequencing Depth", y = "Alpha Diversity")

@@

## Richness

### Plot

@@

### Hypothesis Test

@@

min_seqs <- paste(substr(as.character(min_seqs), 1, 3), substr(as.character(min_seqs), 4, 6), sep = ",")
save(kt, wt, rare_median, s5, min_seqs, file = "Output/richness_models.RData")

@@

# Beta Diversity

@@

if(file.exists("Output/rare_dist_bray.rds")) {
  rare_dist_bray <- 
    readRDS("Output/rare_dist_bray.rds")
} else {
  rare_dist_bray <- avgdist(aes_df, dmethod="bray", sample=seq_range[1])
  rare_dist_bray %>% 
    saveRDS("Output/rare_dist_bray.rds")
}

@@

save(p_beta, file = "Output/beta_fig.RData")

ggsave('Manuscript/fig3.png', p_beta, height = 2.5, width = 4)

ggsave('Manuscript/fig3.svg', p_beta, height = 2.5, width = 4)

@@

save(tidy_permanova, file = "Output/beta_model.RData")

@@

## dbrda methane in passage 5

@@

if(file.exists("Output/rare_dist_bray_p5.rds")) {
  rare_dist_bray_p5 <- 
    readRDS("Output/rare_dist_bray_p5.rds")
} else {
rare_dist_bray_p5 <- avgdist(passage5_df, dmethod="bray", sample=seq_range[1])
  rare_dist_bray_p5 %>% 
    saveRDS("Output/rare_dist_bray_p5.rds")
}

@@

save(dbrda_aov, dbrda_percent_explained, file = "Output/dbrda.RData")

@@

# Differential Abundance

## Unique to each treatment

@@

### Genus

@@

### Species

@@

@@

if(file.exists("Output/ancom_out.rds")) {
  out <- 
    readRDS("Output/ancom_out.rds")
} else {
  # Run Ancom
  out = ancom(phyloseq = aes_ps,  
              p_adj_method = "BH",
              prv_cut = 0.1, 
              lib_cut = 0, 
              main_var = "treat",
              rand_formula = NULL, 
              lme_control = NULL,
              struc_zero = TRUE, 
              neg_lb = FALSE, 
              alpha = 0.05, 
              n_cl = 1)  
  out %>% 
    saveRDS("Output/ancom_out.rds")
}

@@

if(file.exists("Output/aldex_x_all.rds")) {
  x.all <- 
    readRDS("Output/aldex_x_all.rds")
} else {
  x.all <- aldex(otu_table, 
                 conds, mc.samples=1000, test="t", effect=TRUE,
                 include.sample.summary=FALSE, denom="all", verbose=FALSE, paired.test=FALSE)
  x.all %>% 
    saveRDS("Output/aldex_x_all.rds")
}

@@

save(p_log10, da_fams, file = "Output/da_fig.RData")

ggsave('Manuscript/fig4.jpg', p_log10, width = 5, height = 5) 
ggsave('Manuscript/fig4.svg', p_log10, width = 5, height = 5)

## All
# ggsave("shared_taxa.png", p)
# ggsave("shared_taxa_log.png", p_log10, width = 5, height = 5)

@@

```{r corncob-methanotrophs}
if(file.exists("Output/cc_family.rds")) {
  cc_family <- 
    readRDS("Output/cc_family.rds")
} else {
cc_family <- differentialTest(formula = ~ treat,
                                phi.formula = ~ 1,
                                formula_null = ~ 1,
                                phi.formula_null = ~ 1,
                                test = "Wald", 
                                boot = TRUE,
                                data = troph_data_family,
                                sample_data = sample_data,
                                fdr_cutoff = 0.05, B = 1000)  
cc_family %>% 
    saveRDS("Output/cc_family.rds")
}

@@

if(file.exists("Output/cc_genus.rds")) {
  cc_genus <- 
    readRDS("Output/cc_genus.rds")
} else {
cc_genus <- differentialTest(formula = ~ treat,
                                phi.formula = ~ 1,
                                formula_null = ~ 1,
                                phi.formula_null = ~ 1,
                                test = "Wald", 
                                boot = TRUE,
                                data = troph_data_genus,
                                sample_data = sample_data,
                                fdr_cutoff = 0.05, B = 1000) 
cc_genus %>% 
    saveRDS("Output/cc_genus.rds")
}

>>>>

---
title: "Analysis"
author: "Andrew Morris"
date: "2022-11-21"
output: 
    html_document:
        toc: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
here::i_am("analysis/analysis.Rmd")

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = TRUE)

@@

```{r initialize_packages, message=FALSE}
library(morris)
library(broom)
library(knitr)
library(broman)

library(phyloseq)
library(knitr)
library(magrittr)
library(vegan)
library(ggpubr)
library(ggtext)
library(ALDEx2)
library(corncob)
library(ANCOMBC)
library(tidyverse)
library(here)

source(here('R/', 'functions.R'))

set.seed(1337)
```

```{r import_data, message=FALSE}
fluxes <- read_tsv(here(der_dir, 'fluxes.tsv'))
heritability <- read_tsv(here(der_dir, 'heritability.tsv'))
aes_data <- read_tsv(here(der_dir, 'community_data.tsv'))

# Shift the passage numbers so the first passage becomes "Passage 0"
fluxes <-
  fluxes %>% 
  mutate(passage = passage - 1)
```

# Overview

The final dataset includes `r length(unique(fluxes$treat))` treatments across `r length(unique(fluxes$passage))` passages (generations). This includes a total of n = `r nrow(fluxes)` samples. The samples are broken down across passages and treatments as in the following table:

```{r}
fluxes %>% 
  group_by(flux_date, treat) %>% 
  summarize(n = n_distinct(rep), .groups='drop') %>% 
  kable()
```

# Reponse to Selection

This script takes in the flux data. It then plots the raw data
and the log-transformed data. Finally, it fits a linear model to the flux data
over time per treatment and tests a difference of slope between the positive
and the neutral treatment.

## Plot the raw data

```{r plot_raw}
ratio <- calc_plot_ratios(fluxes$passage, fluxes$ch4)

ggplot(fluxes, aes(x = passage, y = ch4, color = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    scale_color_manual(
        name = "Treatment", 
        labels = c('Neutral', 'Positive'), 
        values = c('gray40', 'darkorange2')) +
    geom_jitter(width = 0.1) + 
    labs(x = "Passage Number", 
         y = "Methane Oxidation Rate (-k)") +
    coord_fixed(ratio) +
  scale_x_continuous(labels = 1:5)
```

## Plot the log-transformed data

```{r plot_log10}
ratio_log10 <- calc_plot_ratios(fluxes$passage, fluxes$log_ch4)

(p_response <- ggplot(fluxes, aes(x = passage, y = log_ch4, color = treat)) +
    stat_smooth(method = 'lm', se = FALSE, formula = 'y ~ x') +
    scale_color_manual(
      name = "Treatment", 
      labels = c('Neutral', 'Positive'), 
      values = c('gray40', 'darkorange2')) +
    geom_jitter(#aes(alpha = selected), 
      width = 0.1) + 
        labs(x = "Passage Number", 
                  y = expression(log[10] ~ CH[4] ~ "(-k)")) +
        coord_fixed(ratio_log10) +
  scale_x_continuous(labels = 1:5))

save(p_response, file = here(der_dir, 'response_plot.RData'))

# ggsave(here(fig_dir, 'fig1.jpg'), p_response, width = 4, height = 3) 
# ggsave(here(fig_dir, 'fig1.svg'), p_response, width = 4, height = 3)

@@

## Test a difference of slopes

```{r raw_model}
raw_model <- lm(ch4 ~ passage * treat, data = fluxes)

ggplot(raw_model, aes(x = .fitted, y = .resid)) + geom_point()

@@

```{r response_model}

response_model <- lm(log_ch4 ~ passage * treat, data = fluxes)

ggplot(response_model, aes(x = .fitted, y = .resid)) + geom_point()

# Percent increase in CH4 per passage
# Back calculate the slope of the positive treatment

pos_slope <- 
    response_model$coef[["passage:treatp"]]

per_slope <-
    (10^pos_slope - 1) * 100

```{r no_treat_model}
# No treatment model
no_treat_model <- lm(log_ch4 ~ passage, data = fluxes)

Here I fit two models. The first is the full model which includes passage number, treatment, and the interaction between the two. The second model includes only passage with no effect of treatment. Comparing the models using `anova`

```{r compare_models}
# Compare interaction to no interaction
compare_response_mods <- anova(no_treat_model, response_model)
compare_response_mods <- tidy(compare_response_mods)
kable(compare_response_mods)
```

Here is the full interaction model:

```{r print_model}
kable(tidy(response_model))
```

```{r save_model}
save(response_model, compare_response_mods, per_slope, file = here(der_dir, 'response_model.RData'))
```

The intercept for the Neutral treatment was significantly different from zero
at `r myround(tidy(response_model)[[1, 2]], 2)` 
(SE = `r myround(tidy(response_model)[[1, 3]], 2)`, 
t = `r myround(tidy(response_model)[[1, 4]], 2)`, 
p = `r myround(tidy(response_model)[[1, 5]], 2)`). 
The Positive
treatment started at a significantly lower methane oxidation rate than the
Neutral treatment with a y-intercept of 
`r myround(tidy(response_model)[[3, 2]], 2)` relative to Neutral 
(SE = `r myround(tidy(response_model)[[3, 3]], 2)`, 
t = `r myround(tidy(response_model)[[3, 4]], 2)`, 
p = `r myround(tidy(response_model)[[3, 5]], 2)`). 
There was no change in methane oxidation rate of the Neutral
treatment over the five passages 
(slope = `r myround(tidy(response_model)[[2, 2]], 2)`, 
SE = `r myround(tidy(response_model)[[2, 3]], 2)`, 
t = `r myround(tidy(response_model)[[2, 4]], 2)`, 
p = `r myround(tidy(response_model)[[2, 5]], 2)`). 
By contrast, there was a significant increase in the Positive
treatment of `r myround(tidy(response_model)[[4, 2]], 2)` per passage which is
approximately a `r round((pos_slope - 1) * 100, 0)`% increase in methane
oxidation rate per passage 
(SE = `r myround(tidy(response_model)[[4, 3]], 2)`, 
t = `r myround(tidy(response_model)[[4, 4]], 2)`, 
p = `r myround(tidy(response_model)[[4, 5]], 2)`).

# Heritability

This script imports the heritability data. This dataset includes the mean flux
within treatment by generation for 1) all parents, 2) selected parents, and 3)
offspring. Then, it plots offspring on the selected parents with the two
treatments combined and then separately for the two treatments.

## Test heritability as mid-offspring on mid-parent

```{r test_treatment}

fit_no_treat <- lm(offspring ~ selected, data = heritability)
kable(tidy(fit_no_treat))
herit_model <- lm(offspring ~ selected * treat, data = heritability)
kable(tidy(herit_model))
kable(tidy(anova(fit_no_treat, herit_model)))
summary(herit_model)

herit_model_n <- 
heritability %>% 
  filter(treat == "n") %>% 
  lm(offspring ~ selected, data = .) %>% 
  tidy()
herit_model_n
herit_model_p <- 
heritability %>% 
  filter(treat == "p") %>% 
  lm(offspring ~ selected, data = .)
summary(herit_model_p)
```

Here, I fit two models. The first is simply offspring flux on selected parent flux, ignoring treatment. There is no correlation `r print_lm(fit_no_treat, 2)`. Next, I added treatment and the interaction between treatment and parental flux. Here, there is a significant correlation between parent and offspring for both the Neutral treatment `r print_lm(herit_model, 2)` and the Positive treatment `r print_lm(herit_model, 4)`. Notably, the sign of the effect is reversed: negative for the Neutral treatment and positive for the Positive treatment.

```{r plot_herit}

n_label <- paste0('Neutral slope = ', myround(tidy(herit_model)[2, 2], 2))
p_label <- paste0('Positive slope = ', myround(tidy(herit_model)[2, 2] + tidy(herit_model)[4, 2], 2))
  ratio <- calc_plot_ratios(heritability$selected, heritability$offspring)
(p_herit <- 
  ggplot(heritability, aes(selected, offspring, color = treat)) +
    geom_point() + 
    # stat_poly_eq() +
    stat_smooth(method = 'lm', se = F) +
    # annotate("text", x = min(heritability$parental), y = max(heritability$offspring), label = p_label, hjust = 0, color = "darkorange2") +
    # annotate("text", x = min(heritability$parental), y = max(heritability$offspring) - 0.04, label = n_label, hjust = 0, color = "gray40") +
    labs(x = expression(Donor ~ log[10] ~ CH[4] ~ "(-k)"), 
         y = expression(atop(Recipient, log[10] ~ CH[4] ~ "(-k)"))) +
    scale_color_manual(name = "Treatment", 
                       labels = c('Neutral', 'Positive'), 
                       values = c('gray40', 'darkorange2')) +
    coord_fixed(1))

save(p_herit, file = here(der_dir, 'herit_plot.RData'))

# ggsave(here(fig_dir, 'fig2.jpg'), p_herit, width = 4, height = 3)
# ggsave(here(fig_dir, 'fig2.svg'), p_herit, width = 4, height = 3)

```{r save_heritability}
save(herit_model, file = here(der_dir, 'herit_model.RData'))
```

```{r}
heritability_each <- read_tsv(here(der_dir, 'heritability_each.tsv'))

fit_no_treat <- lm(offspring ~ selected, data = heritability_each)
kable(tidy(fit_no_treat))
herit_model <- lm(offspring ~ selected * treat, data = heritability_each)
kable(tidy(herit_model))
kable(tidy(anova(fit_no_treat, herit_model)))

herit_model_n_each <- 
heritability_each %>% 
  filter(treat == "n") %>% 
  lm(offspring ~ selected, data = .) %>% 
  tidy()
herit_model_p_each <- 
heritability_each %>% 
  filter(treat == "p") %>% 
  lm(offspring ~ selected, data = .) %>% 
  tidy()

ratio <- calc_plot_ratios(heritability_each$selected, heritability_each$offspring)
(p_herit_each <- 
ggplot(heritability_each, aes(selected, offspring, color = treat)) +
    # theme_classic() +
    # geom_rangeframe(color = 'black') +
    geom_point() + 
    stat_smooth(method = 'lm', se = F) +
    # stat_poly_line(se = T) +
    # stat_poly_eq(aes(label = paste(after_stat(eq.label),
                                 # after_stat(rr.label), sep = "*\", \"*"))) +
    labs(x = expression(atop(Mean ~ Donor, log[10] ~ CH[4] ~ "(-k)")), 
         y = expression(atop(Recipient, log[10] ~ CH[4] ~ "(-k)"))) +
    scale_color_manual(name = "Treatment", 
                       labels = c('Neutral', 'Positive'), 
                       values = c('gray40', 'darkorange2')) +
    coord_fixed(1))

# save(p_herit_each, file = here(der_dir, 'herit_plot.RData'))
# save(herit_model, file = here(der_dir 'herit_model.RData'))
# 
# ggsave(here(fig_dir, 'fig2_each.jpg'), p_herit_each, width = 4, height = 3) 
# ggsave(here(fig_dir, 'fig2_each.svg'), p_herit_each, width = 4, height = 3) 
```

# Community Analysis

@@

```{r remove_chloroplasts_mitochondria}

@@

mitochondria_seqs <-
  aes_data %>% 
  filter(Family == 'Mitochondria') %>%
  select(asv, seq) %>% 
  distinct() %$%
  seq

# 99 ASVs were identified as Mitochondria

aes_data <- 
  aes_data %>% 
  filter(Family != 'Mitochondria')

@@

## Exploratory

@@

@@

### Richness

#### Plot

@@

#### Hypothesis Test

@@

min_seqs <- paste(substr(as.character(min_seqs), 1, 3), substr(as.character(min_seqs), 4, 6), sep = ",")
save(kt, wt, rare_median, s5, min_seqs, file = here(der_dir, "richness_models.RData"))

@@

## Beta Diversity

@@

if(file.exists(here(der_dir, "rare_dist_bray.rds"))) {
  rare_dist_bray <- 
    readRDS(here(der_dir, "rare_dist_bray.rds"))
} else {
  rare_dist_bray <- avgdist(aes_df, dmethod="bray", sample=seq_range[1])
  rare_dist_bray %>% 
    saveRDS(here(der_dir, "rare_dist_bray.rds"))
}

@@

save(p_beta, file = here(der_dir, "beta_fig.RData"))

ggsave(here(fig_dir, 'fig3.png'), p_beta, height = 2.5, width = 4)

ggsave(here(fig_dir, 'fig3.svg'), p_beta, height = 2.5, width = 4)

@@

save(tidy_permanova, file = here(der_dir, "beta_model.RData"))

@@

### dbrda methane in passage 5

@@

if(file.exists(here(der_dir, "rare_dist_bray_p5.rds"))) {
  rare_dist_bray_p5 <- 
    readRDS(here(der_dir, "rare_dist_bray_p5.rds"))
} else {
rare_dist_bray_p5 <- avgdist(passage5_df, dmethod="bray", sample=seq_range[1])
  rare_dist_bray_p5 %>% 
    saveRDS(here(der_dir, "rare_dist_bray_p5.rds"))
}

@@

save(dbrda_aov, dbrda_percent_explained, file = here(der_dir, "dbrda.RData"))

@@

## Differential Abundance

### Unique to each treatment

#### Family

@@

#### Genus

@@

#### Species

@@

```{r}
# 
# # Install ANCOMBC
# if (!requireNamespace("BiocManager", quietly=TRUE))
#     install.packages("BiocManager")
# BiocManager::install("ANCOMBC")
# 
# # Load ANCOM
# library(ANCOMBC)

@@

# Save/Load output so you don't have to rerun ANCOM
if(file.exists(here(der_dir, "ancom_out.rds"))) {
  out <- 
    readRDS(here(der_dir, "ancom_out.rds"))
} else {
  # Run Ancom
  out = ancom(phyloseq = aes_ps,  
              p_adj_method = "BH",
              prv_cut = 0.1, 
              lib_cut = 0, 
              main_var = "treat",
              rand_formula = NULL, 
              lme_control = NULL,
              struc_zero = TRUE, 
              neg_lb = FALSE, 
              alpha = 0.05, 
              n_cl = 1)  
  out %>% 
    saveRDS(here(der_dir, "ancom_out.rds"))
}

@@

if(file.exists(here(der_dir, "aldex_x_all.rds"))) {
  x.all <- 
    readRDS(here(der_dir, "aldex_x_all.rds"))
} else {
  x.all <- aldex(otu_table, 
                 conds, mc.samples=1000, test="t", effect=TRUE,
                 include.sample.summary=FALSE, denom="all", verbose=FALSE, paired.test=FALSE)
  x.all %>% 
    saveRDS(here(der_dir, "aldex_x_all.rds"))
}

@@

save(p_log10, da_fams, file = here(der_dir, "da_fig.RData"))

ggsave(here(fig_dir, 'fig4.jpg'), p_log10, width = 5, height = 5) 
ggsave(here(fig_dir, 'fig4.svg'), p_log10, width = 5, height = 5)

## All
# ggsave(here(fig_dir, "shared_taxa.png"), p)
# ggsave(here(fig_dir, "shared_taxa_log.png"), p_log10, width = 5, height = 5)

@@

```{r corncob-methanotrophs}
if(file.exists(here(der_dir, "cc_family.rds"))) {
  cc_family <- readRDS(here(der_dir, "cc_family.rds"))
} else {
cc_family <- differentialTest(formula = ~ treat,
                                phi.formula = ~ 1,
                                formula_null = ~ 1,
                                phi.formula_null = ~ 1,
                                test = "Wald", 
                                boot = TRUE,
                                data = troph_data_family,
                                sample_data = sample_data,
                                fdr_cutoff = 0.05, B = 1000)  
cc_family %>% saveRDS(here(der_dir, "cc_family.rds"))
}

@@

if(file.exists(here(der_dir, "cc_genus.rds"))) {
  cc_genus <- 
    readRDS(here(der_dir, "cc_genus.rds"))
} else {
cc_genus <- differentialTest(formula = ~ treat,
                                phi.formula = ~ 1,
                                formula_null = ~ 1,
                                phi.formula_null = ~ 1,
                                test = "Wald", 
                                boot = TRUE,
                                data = troph_data_genus,
                                sample_data = sample_data,
                                fdr_cutoff = 0.05, B = 1000) 
cc_genus %>% 
    saveRDS(here(der_dir, "cc_genus.rds"))
}

### 2022-12-06 manuscript/manuscript.Rmd
reorganize working directory and add new analysis and text

The initial soil microbiome was sampled from the top 10 cm of an upland mineral
soil under a deciduous forest ecosystem near the University of Oregon campus in
Eugene, OR, USA. Incubations were performed in 500 mL mason jars with rubber
septa installed in the lids. Each jar was sterilized with 70\% ethanol to which
was added 45 g of autoclaved potting mix, 5 g of living soil, and 3.5 mL of
sterile deionized water to bring them to 60\% of field capacity. The potting
mix was Lane Potting Mix from Lane Forest Products (Eugene, OR, USA). Each jar
was then capped and injected with 4.3 mL of 99\% CH~4~ to bring
the headspace concentration to approximately 1000 ppm CH~4~. To create the two
treatment groups, twenty-four jars were created in an identical manner and then
randomly assigned to either the positive or neutral selection line. Jars were
flushed and respiked with methane twice per week to maintain aerobic conditions and elevated
CH~4~ concentrations and were incubated at ambient temperature for
approximately three weeks. Methane oxidation rates were determined at the end
of the incubation period. For the positive treatment, the three jars with the
greatest CH~4~ oxidation rates were chosen to inoculate the next generation.
For the neutral treatment, three jars were randomly selected to inoculate the
next generation. For each treatment, the selected jars were homogenized and 5 g
of the homogenized soil was used to inoculate the next set of jars, which
represents a 10% subsampling. The next set of jars were created in an identical
manner to the first generation with fresh autoclaved potting mix and the same
moisture and CH~4~ content.

>>>>

The initial soil microbiome was sampled from the top 10 cm of an upland mineral
soil under a deciduous forest ecosystem near the University of Oregon campus in
Eugene, OR, USA. Incubations were performed in 500 mL mason jars with rubber
septa installed in the lids. Each jar was sterilized with 70\% ethanol to which
was added 45 g of autoclaved potting mix, 5 g of living soil, and 3.5 mL of
sterile deionized water to bring them to 60\% of field capacity. The potting
mix was Lane Potting Mix from Lane Forest Products (Eugene, OR, USA). Each jar
was then capped and injected with 4.3 mL of 99\% CH~4~ to bring
the headspace concentration to approximately 1000 ppm CH~4~. To create the two
treatment groups, twenty-four jars were created in an identical manner and then
randomly assigned to either the positive or neutral selection line. Jars were
flushed and respiked with methane twice per week to maintain aerobic conditions and elevated
CH~4~ concentrations and were incubated at ambient temperature for
approximately four weeks. Methane oxidation rates were determined at the end
of the incubation period. For the positive treatment, the three jars with the
greatest CH~4~ oxidation rates were chosen to inoculate the next generation.
For the neutral treatment, three jars were randomly selected to inoculate the
next generation. For each treatment, the selected jars were homogenized and 5 g
of the homogenized soil was used to inoculate the next set of jars, which
represents a 10% subsampling. The next set of jars were created in an identical
manner to the first generation with fresh autoclaved potting mix and the same
moisture and CH~4~ content.
